DRAFT_secondtrailopening

### 2021-08-23 R/DRAFT_secondtrailsopening.Rmd

    for (accessid in unique(pts$ID)) {

      selectedPoints <- pts %>% filter(ID == accessid) 
      PointAcc <- selectedPoints %>% filter(type == "Access") %>% 
        mutate(ptAcc = dplyr::row_number()) %>% 
        mutate(EstCost = NA)
      CostDistEst <- AdjTopoLCP(costSurface = CondSurf,
                                DEM = DEMmean , 
                                pts = selectedPoints %>% 
                                  as_Spatial(),
                                slopeRdCond = SlopeCond,
                                paths = FALSE) [,1:dim(PointAcc)[1]]
      CostDistEst[CostDistEst == 0] <- NA
      CostDistEst <- na.exclude(CostDistEst)
      PointTree <- selectedPoints %>% filter(type == "Tree") %>% 
        mutate(ptAcc = max.col(-CostDistEst))
      if (dim(PointAcc)[1] == 1) {
        PointTree <- PointTree %>% mutate(EstCost = CostDistEst)
      }else{PointTree <- PointTree %>% mutate(EstCost = apply(CostDistEst,1, min))}
      selectedPoints <- rbind(PointAcc,PointTree)

@@

            pathLines[[k]] <- TmpPathWIP[[2]]
            pathLines[[k]]@lines[[1]]@ID <- paste("Path",accessid,"-",accessPtId, "-", TreeId, sep = " ")

          }
        }
      }

@@

>>>>

  CostDistEst <- AdjTopoLCP(costSurface = CondSurf,
                                DEM = DEMmean , 
                                pts = pts %>% 
                                  as_Spatial(),
                                slopeRdCond = SlopeCond,
                                paths = FALSE) [,1:dim(AccessPoint)[1]]
  CostDistEst <- CostDistEst[(dim(PointAcc)[1]+1):dim(CostDistEst)[1],1:dim(PointAcc)[1]]

  CostDistEst <- matrix(CostDistEst,ncol = dim(PointAcc)[1] )

  PointTree <- pts %>% filter(type == "Tree") %>% 
      mutate(ptAcc = max.col(-CostDistEst))
  PointTree$ID <- as.factor(PointTree$ptAcc)
  levels(PointTree$ID) <- as.character(AccessPoint$ID)

  pts <- rbind(AccessPoint %>% 
                 mutate(type = "Access") %>% 
                 mutate(ptAcc = row_number()) %>% 
                 mutate(IPpts = paste0("A.",row_number())),
               PointTree %>% 
                 mutate(IPpts = paste0("T.",row_number())))

  PointAcc <- pts %>% filter(type == "Access") %>% 
        mutate(EstCost = NA)

  CostDistEst <- AdjTopoLCP(costSurface = CondSurf,
                                DEM = DEMmean , 
                                pts = pts %>% 
                                  as_Spatial(),
                                slopeRdCond = SlopeCond,
                                paths = FALSE) [,1:dim(PointAcc)[1]]
  CostDistEst <- CostDistEst[(dim(PointAcc)[1]+1):dim(CostDistEst)[1],1:dim(PointAcc)[1]]

  CostDistEst <- matrix(CostDistEst,ncol = dim(PointAcc)[1] )

  PointTree <- pts %>% filter(type == "Tree") %>% 
        mutate(ptAcc = max.col(-CostDistEst))
  if (dim(PointAcc)[1] == 1) {
      PointTree <- PointTree %>% mutate(EstCost = CostDistEst)
    }else{PointTree <- PointTree %>% mutate(EstCost = apply(CostDistEst,1, min))}
  selectedPoints <- rbind(PointAcc,PointTree)

@@

      }
    }
   }
  }else{

    # winching == 1/2

    PointAcc <- AccessPoint %>% #def Access Point
      mutate(type = "Access") %>% 
      mutate(IDpts = paste0("A.",row_number())) %>% 
      mutate(n.overlaps = NA, origins = NA) %>% 
      dplyr::select(-ID)

    if (winching == "2") {
      ptsGrpl <- pts %>% filter(type == "Tree") %>% #def Grpl point
                  st_buffer(dist = advancedloggingparameters$GrappleLength) %>%
                  st_set_precision(1) %>% 
                  st_intersection() %>% 
                  st_make_valid()

       ptsGrpl <- ptsGrpl %>%  filter(st_intersects(ptsGrpl ,AccessMainTrails %>% st_union(),sparse = FALSE)) %>% 
                  mutate(IDpts = paste0("I.",row_number()))

       ptsWIP <- ptsGrpl %>% #def Grpl point as WIP point
                  st_centroid() %>% 
                  dplyr::select(-ID)

       ptsCbl <- pts %>% filter(type == "Tree") %>% #def cbl point
                  st_buffer(dist = advancedloggingparameters$CableLength) %>%
                  st_set_precision(1) %>% 
                  st_intersection() %>% 
                  st_make_valid()

        ptsCbl <- ptsCbl %>% 
                  filter(st_intersects(ptsCbl ,AccessMainTrails %>% st_union() ,sparse = FALSE)) %>% 
                  mutate(IDpts = paste0("I.",row_number()))

        ptsWIPCbl <-  ptsCbl %>%
          st_centroid() %>%
          dplyr::select(-ID)

        ptsWIP <- ptsWIP %>% 
                  arrange(desc(n.overlaps))

        RemainTree <- dim(ptsWIP %>% filter(type == "Tree"))[1] + dim(ptsWIPCbl %>% filter(type == "Tree"))[1]

    }else{
        ptsCbl <- pts %>% filter(type == "Tree") %>% #def cbl point
                  st_buffer(dist = advancedloggingparameters$CableLength) %>%
                  st_set_precision(1) %>% 
                  st_intersection() %>% 
                  st_make_valid() %>% 
                  mutate(IDpts = paste0("I.",row_number()))

        ptsWIP <-  ptsCbl %>%#def cbl point as WIP point
          st_centroid() %>%
          dplyr::select(-ID)

        ptsWIP <- ptsWIP %>%  #filter cbl intersection centroid point out plot
                  filter(st_intersects(ptsWIP ,Plots %>% st_as_sf(),sparse = FALSE)) %>% 
                  arrange(desc(n.overlaps))

        RemainTree <- dim(ptsWIP %>% filter(type == "Tree"))[1]

    limRec <- dim(pts)[1]

    WinchingSwitch <- FALSE

    while (RemainTree !=0L & k <= limRec) {

      Grpl2CblFlag <- FALSE

      print(paste0("iter : ",k, "| Max : ",limRec) )

    ptsWIPmax <- rbind(PointAcc,ptsWIP %>% 
                         filter(n.overlaps == max(ptsWIP$n.overlaps))) %>% 
              mutate(TypeAcc = NA) %>% 
              mutate(EstCost = NA)  %>% 
              mutate(ptsAcc = NA)

    CostDistEstCbl <- AdjTopoLCP(costSurface = CondSurf,
                                DEM = DEMmean , 
                                pts = ptsWIPmax %>% 
                                  as_Spatial(),
                                slopeRdCond = SlopeCond,
                                paths = FALSE) [,1:dim(PointAcc)[1]]

    CostDistEstCbl <- CostDistEstCbl[(dim(PointAcc)[1]+1):dim(CostDistEstCbl)[1],1:dim(PointAcc)[1]]

    CostDistEstCbl <- matrix(CostDistEstCbl,ncol = dim(PointAcc)[1] )

    PointTree <- ptsWIPmax %>% filter(type == "Tree") %>% 
        mutate(ptAccCbl = max.col(- CostDistEstCbl,ties.method = "first"))

    if (dim(PointAcc)[1] == 1) {
      PointTree <- PointTree %>% mutate(EstCostCbl = CostDistEstCbl)
    }else{
      PointTree <- PointTree %>% mutate(EstCostCbl = apply(CostDistEstCbl,1, min))
      }

        CondSurfGrpl <- 1/CostRasterMeanGrpl

        CostDistEstGrpl <- AdjTopoLCP(costSurface = CondSurfGrpl,
                                DEM = DEMmean , 
                                pts = ptsWIPmax %>% 
                                  as_Spatial(),
                                slopeRdCond = SlopeCond,
                                paths = FALSE) [,1:dim(PointAcc)[1]]

        CostDistEstGrpl <- CostDistEstGrpl[(dim(PointAcc)[1]+1):dim(CostDistEstGrpl)[1],1:dim(PointAcc)[1]]
        CostDistEstGrpl <- matrix(CostDistEstGrpl,ncol = dim(PointAcc)[1] )

        PointTree <- PointTree %>% 
          mutate(ptAccGpl = max.col(-matrix(CostDistEstGrpl,ncol = dim(PointAcc)[1] ),ties.method = "first"))

          if (dim(PointAcc)[1] == 1) {
            PointTree <- PointTree %>% mutate(EstCostGrpl = CostDistEstGrpl)
          }else{
              PointTree <- PointTree %>% mutate(EstCostGrpl = apply(matrix(CostDistEstGrpl,ncol = dim(PointAcc)[1] ),1, min))}

        CostDistEstGrpl[CostDistEstGrpl != Inf] <- 0
        CostDistEstGrpl[CostDistEstGrpl == Inf] <- 1

        for (j in 1:dim(CostDistEstGrpl)[1]) {
          PointTree[j,"TypeAcc"] <-  as.character(prod(CostDistEstGrpl[j,]))
        }
        PointTree$TypeAcc[PointTree$TypeAcc == "0"] <- "Grpl"
        PointTree$TypeAcc[PointTree$TypeAcc == "1"] <- "Cbl"

        PointTree$ptsAcc[PointTree$TypeAcc == "Grpl"] <- PointTree$ptAccGpl[PointTree$TypeAcc == "Grpl"]
        PointTree$ptsAcc[PointTree$TypeAcc != "Grpl"] <- PointTree$ptAccCbl[PointTree$TypeAcc != "Grpl"]

        PointTree$EstCost[PointTree$TypeAcc == "Grpl"] <- PointTree$EstCostGrpl[PointTree$TypeAcc == "Grpl"]
        PointTree$EstCost[PointTree$TypeAcc != "Grpl"] <- PointTree$EstCostCbl[PointTree$TypeAcc != "Grpl"]

        PointTree <- PointTree %>% arrange(desc(TypeAcc),EstCost)

            if (PointTree$TypeAcc[1] == "Grpl") {

              TmpPtsWIP <- ptsGrpl %>% 
                                filter(IDpts == PointTree$IDpts[1])  %>%  
                                st_union() %>% 
                                st_cast("POINT") %>% 
                                st_as_sf() %>%
                                mutate(type = "Overlay") %>% 
                                mutate(ptsAcc = PointTree$ptsAcc[1]) %>% 
                                mutate(IDpts = PointTree$IDpts[1]) %>% 
                                mutate(origins = PointTree$origins[1])

              }else{

            Grpl2CblFlag <- TRUE

            ptsWIP$Logged<- FALSE

            for (j in 1:dim(ptsWIP)[1]) {
              ptsWIP$Logged[j] <- prod(as.integer(PointTree$origins[1][[1]] %in% ptsWIP$origins[[j]])+1) != 1
            }

            ptsWIP[ptsWIP$Logged == TRUE,"Logged"] <- NA
            ptsWIP <- na.exclude(ptsWIP)

            ptsWIP <- ptsWIP %>% 
              dplyr::select(-Logged) %>% 
              arrange(desc(n.overlaps))

            TmpPtsWIP <- ptsCbl %>% 
                                filter(IDpts == PointTree$IDpts[1])  %>%  
                                st_union() %>% 
                                st_cast("POINT") %>% 
                                st_as_sf() %>%
                                mutate(type = "Overlay") %>% 
                                mutate(ptsAcc = PointTree$ptsAcc[1]) %>% 
                                mutate(IDpts = PointTree$IDpts[1]) %>% 
                                mutate(origins = PointTree$origins[1])
              }

      }else{

        TmpPtsWIP <- ptsCbl %>% 
                                filter(IDpts == PointTree$IDpts[1])  %>%  
                                st_union() %>% 
                                st_cast("POINT") %>% 
                                st_as_sf() %>%
                                mutate(type = "Overlay") %>% 
                                mutate(ptsAcc = PointTree$ptsAcc[1]) %>% 
                                mutate(IDpts = PointTree$IDpts[1]) %>% 
                                mutate(origins = PointTree$origins[1])

              TmpPtsWIP <- TmpPtsWIP  %>%  
                                filter(st_intersects(TmpPtsWIP,AccessMainTrails %>% st_union(),sparse = FALSE))

              TmpPtsWIP <- rbind(PointAcc %>%  
                                st_union() %>% 
                                st_cast("POINT")%>% 
                                st_as_sf() %>% 
                                mutate(type = "Access") %>% 
                                mutate(ptsAcc = NA ) %>% 
                                mutate(IDpts = NA) %>% 
                                mutate(origins = NA),TmpPtsWIP)

            CostDistEstWIP <-  AdjTopoLCP(costSurface = CondSurf,DEM = DEMmean , pts = TmpPtsWIP %>% as_Spatial(),
                              slopeRdCond = SlopeCond,paths = FALSE)[,1:dim(PointAcc)[1]]

            CostDistEstWIP <- CostDistEstWIP[(dim(PointAcc)[1]+1):dim(CostDistEstWIP)[1],]

            CostDistEstWIP <- matrix(CostDistEstWIP, ncol = dim(PointAcc)[1])

          if (dim(PointAcc)[1] == 1) {
            PointTreeWIP <- TmpPtsWIP %>% 
              filter(type == "Overlay") %>% 
              mutate(EstCost = CostDistEstWIP) %>% 
              arrange(EstCost)
          }else{

            PointTreeWIP <- TmpPtsWIP %>% 
                filter(type == "Overlay") %>% 
                mutate(EstCost = apply(CostDistEstWIP,1, min)) %>% 
                arrange(EstCost)

            TmpPathWIP <- AdjTopoLCP(costSurface = CondSurf,DEM = DEMmean , pts = TmpPtsWIP %>% as_Spatial(),
                              slopeRdCond = SlopeCond,paths = FALSE)

            TmpPathWIPCost <- TmpPathWIP[1:dim(PointAcc)[1],dim(PointAcc)[1]+1]

            LCPathWIP <- max.col(t(-TmpPathWIPCost))

            TmpPtsWIP <- rbind(TmpPtsWIP[LCPathWIP,],PointTreeWIP[1,])

            CostRasterMean  <- rasterize(x = TmpPathWIP[[2]] ,
                                    y = CostRasterMean  , 
                                    field = 0.3,update =  TRUE)

            pathLines[[k]] <- TmpPathWIP[[2]]
            pathLines[[k]]@lines[[1]]@ID <- paste("Path",
                                                  LCPathWIP,
                                                  "-",
                                                  paste(as.character(unlist(PointTreeWIP$origins[1][[1]])), 
                                                        collapse='.'), 
                                                  sep = " ")

             if (Grpl2CblFlag) {

               ptsWIPCbl$Logged<- FALSE
              for (j in 1:dim(ptsWIPCbl)[1]) {
              ptsWIPCbl$Logged[j] <- prod(as.integer(PointTreeWIP$origins[1][[1]] %in% ptsWIPCbl$origins[[j]])+1) != 1
              }
                          ptsWIPCbl[ptsWIPCbl$Logged == TRUE,"Logged"] <- NA
            ptsWIPCbl <- na.exclude(ptsWIPCbl)
                        ptsWIPCbl <- ptsWIPCbl %>% 
              dplyr::select(-Logged) %>% 
              arrange(desc(n.overlaps))
             }else{

            ptsWIP$Logged<- FALSE

            for (j in 1:dim(ptsWIP)[1]) {
              ptsWIP$Logged[j] <- prod(as.integer(PointTreeWIP$origins[1][[1]] %in% ptsWIP$origins[[j]])+1) != 1
            }

                        ptsWIP[ptsWIP$Logged == TRUE,"Logged"] <- NA
            ptsWIP <- na.exclude(ptsWIP)

            ptsWIP <- ptsWIP %>% 
              dplyr::select(-Logged) %>% 
              arrange(desc(n.overlaps))

              ptsWIPCbl$Logged<- FALSE
              for (j in 1:dim(ptsWIPCbl)[1]) {
              ptsWIPCbl$Logged[j] <- prod(as.integer(PointTreeWIP$origins[1][[1]] %in% ptsWIPCbl$origins[[j]])+1) != 1
              }
                          ptsWIPCbl[ptsWIPCbl$Logged == TRUE,"Logged"] <- NA
            ptsWIPCbl <- na.exclude(ptsWIPCbl)
                        ptsWIPCbl <- ptsWIPCbl %>% 
              dplyr::select(-Logged) %>% 
              arrange(desc(n.overlaps))
            }

            if (dim(ptsWIP %>% filter(type == "Tree"))[1] == 0 & WinchingSwitch == FALSE) {
              winching <- "1"
              ptsWIP <- ptsWIPCbl
              WinchingSwitch <- TRUE
            }

            if (winching == "2") {
              RemainTree <- dim(ptsWIP %>% filter(type == "Tree"))[1] + dim(ptsWIPCbl %>% filter(type == "Tree"))[1]
            }else{
             RemainTree <- dim(ptsWIP %>% filter(type == "Tree"))[1] 
            }

@@

```{r}
  paths <- do.call(rbind, pathLines)

    df <-  as_tibble(rasterToPoints(CostRasterMean)) %>% mutate( Cost = layer) %>% dplyr::select(-layer)
  df2 <- as_tibble(rasterToPoints(DEM)) %>% mutate( z = Topo_P6_PARACOU) %>% dplyr::select(-Topo_P6_PARACOU)
  df3 <- as_tibble(rasterToPoints(raster(SlopeCond))) %>% mutate( AccSlp = layer) %>% dplyr::select(-layer)
  ggplot() +
    geom_raster(data = df, aes(x =x , y = y, fill = Cost)) +  geom_sf(data = pts) + scale_fill_gradientn(colours = rev(terrain.colors(225)))  + geom_sf( data = sf::st_as_sf(paths))    + geom_sf(data =  paths %>% st_as_sf()  %>% smoothr::smooth(method = "ksmooth",smoothness = 5) %>% st_buffer(dist = advancedloggingparameters$ScndTrailWidth) %>% st_union(), color = 'red', alpha = 0.1 )  + theme_bw()
```
